Manuscript figures

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 2 for revision"

ggsave(here('docs/figures/figure1_study_area.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 1772, height = 1772)
```

@@

#################### Make the figure ##################
# Satellite images
# Image of season 1
s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 1)") +
    theme_void() +
    theme(plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

@@

## Signatures
# Define colors
cols_lc <- tibble(
    cols = c('#ff7f00', '#074702', '#b2df8a',
             '#33a02c', '#3347f9', '#5a6057',
             '#fdbf6f'),
    `Land cover type` = c("Cropland", 'Forest/dense tree', 
                          "Grassland", 'Shrubland',  "Water", 
                          "Built-up", 'Bareland'),
    ids = as.factor(1:7))

# Burn the color table in
pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
pts_ts <- merge(pts_ts, cols_lc[, 2:3])
pts_fit <- merge(pts_fit, cols_lc[, 2:3])

@@

fg <- ggarrange(images, epl, nrow = 2, heights = c(1, 2.5))
ggsave(here('docs/figures/satellite_images.tiff'),
       fg, bg = "white",
       width = 6, height = 6, dpi = 600)
```

>>>>

# Figure 1, combination art
# Single column figure, 1772 * 1772 at 500 dpi
ggsave(here('docs/figures/figure1_study_area.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 1772, height = 1772)
```

@@

#################### Make the figure ##################
# Define colors
cols_lc <- tibble(
    cols = c('#ff7f00', '#074702', '#b2df8a',
             '#33a02c', '#3347f9', '#5a6057',
             '#fdbf6f'),
    `Land cover type` = c("Cropland", 'Forest/dense tree', 
                          "Grassland", 'Shrubland',  "Water", 
                          "Built-up", 'Bareland'),
    ids = as.factor(1:7))
# Satellite images
# Image of season 1
s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    ggtitle("NICFI (season 1)") +
    theme_void() +
    theme(plot.title = element_text(size = 10, hjust = 0.5),
          plot.margin = unit(rep(-0.1, 4),"cm"))

@@

## Signatures
# Burn the color table in
pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
pts_ts <- merge(pts_ts, cols_lc[, 2:3])
pts_fit <- merge(pts_fit, cols_lc[, 2:3])

@@

fg <- ggarrange(images, epl, nrow = 2, heights = c(1, 2.5))

ggsave(here('docs/figures/satellite_images.tiff'),
       fg, bg = "white", 
       width = 6, height = 6, dpi = 600)

# Figure 2, combination art
# Double column figure, 3740 * 3740 at 500 dpi
ggsave(here('docs/figures/figure2_satellite_images.tiff'),
       main_fg, bg = "white", units = "px", 
       width = 3740, height = 3740)
```
